### 2013-09-06 pystruct/paper.tex
some typos, korrektur lesen....

Unfortunately only few implementations are publicly
available---many applications are based on the non-free implementation
of~\citet{joachims2009cutting}.
We provide an implementation, \pystruct, which aims at providing a high-quality
code with an easy-to-use interface, in the high-level Python language.  This
allows practitioners to efficiently test a range of models, as well as allowing
researchers to compare to baseline methods much more easily than this is
possible with current implementations.  \pystruct is BSD-licensed, allowing
modification and redistribution of the code, as well as use in commercial
applications.  By embracing paradigms established in the scientific Python
community and reusing the interface of the widely-used {\sc scikit-learn}
library~\citep{pedregosa2011scikit}, \pystruct can be used in existing
projects, replacing standard classifiers. The online documentation and
examples help new users understand the somewhat abstract ideas behind
structured prediction.
We will base the experiments in the rest of this work on the algorithms
implemented in \pystruct.

\subsection{Library Structure and Content}
Using the formulation of structured prediction introduced in
\Secref{basics_structured_prediction}, learning can be broken down into three
sub-problems:
\begin{enumerate*}
    \item Encoding the structure of the problem in a joint feature function $\Phi$.
    \item Solving the loss-augmented prediction problem in Equation~\eqref{loss_augmentation}.
    \item Optimizing the objective \Eqref{learning_equation} with respect to $\theta$.
\end{enumerate*}
The first two problems are usually tightly coupled, as the maximization in
Equation~\ref{eq:main_equation} is usually only feasible by exploiting the
structure of $\Phi$, as described in \Secref{factor_graphs}. The last problem,
finding $\theta$, on the other hand, is usually treated as independent.
\pystruct takes an object-oriented approach to decouple the task-dependent
implementation of 2. and 3. from the general algorithms used to solve 1.

Estimating $\theta$ is done in \texttt{learner} classes, which currently
support cutting plane algorithms for structural support vector
machines~(SSVMs), the Block-Coordinate Frank Wolfe (BCFW) algorithm for SSVMs,
subgradient methods for SSVMs, the structured perceptron and latent variable
SSVMs. The cutting plane implementation uses the {\sc cvxopt}
package \citep{dahl2006cvxopt} for quadratic optimization.

@@

Table~\ref{table:comparision_algorithms} lists learning algorithms that are implemented
in \pystruct and compares them to other public structured prediction libraries.
Table~\ref{table:comparision_models} lists

%TODO what about language / license?
\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccccc}
\toprule
Package       & Cutting Plane& SSGD & BCFW & Latent SSVM & Perceptron & ML\\
\cmidrule(r){1-1} \cmidrule(r){2-7}
\pystruct     & \x        & \x   & \x   & \x          & \x         & \o\\
\svmstruct    & \x        & \o   & \o   & \x          & \o         & \o\\
\sc{Dlib}     & \x        & \x   & \o   & \o          & \x         & \o\\
\sc{CRFsuite} & \o        & \o   & \o   & \o          & \x         & \x\\

\bottomrule
\end{tabularx}
    \caption{\label{table:comparision_algorithms}Comparison of learning
        algorithms implemented in popular structured prediction software
        packages. SSGD stochastic subgradient decent learning of SSVMs, BCFW for
    Block-Coordinate Frank-Wolfe, Latent SSVM for latent variable SSVMs, ML for
    maximum likelihood learning}
\end{table}

@@

\paragraph{Testing}
     \pystruct contains a testing-suite with 80\% line-coverage. It also
     employs continuous integration to ensure stability and seamless user
     experience.

@@

The source code is shown in Listing 1.
Lines 1-3 declare a model using parametric edge potentials for arbitrary graphs.
Here \texttt{class\_weight} re-weights the hamming loss according to inverse class
frequencies. The parametric pairwise interactions have three features: a
constant feature, color similarity, and relative vertical position. The first two
are declared to be symmetric with respect to the direction of an edge, the last
is antisymmetric. The inference method used is QPBO-fusion moves.  Line 5
creates a \texttt{learner} object that will learn the parameters for the given
model using the n-slack cutting plane method, and line 6 performs the actual
learning.  Using this simple setup, we achieve an accuracy of 30.3 on the
validation set following the protocol of \citet{krahenbuhl2012efficient}, who
report 30.2 using a more complex approach. Training the structured model takes
approximately 30 minutes using a single i7 core.

\subsection{Experiments}\label{sec:benchmarks}
While \pystruct focuses on usability and covers a wide range of applications, it is also
important that the implemented learning algorithms run in acceptable time.
In this section, we compare our implementation of the one-slack cutting plane
algorithm with the implementation in \svmstruct.
We compare performance of the Crammer-Singer multi-class SVM with respect to
learning time and accuracy on the MNIST dataset of handwritten digits.
While multi-class classification is not very interesting from a structured
prediction point of view, this problem is well-suited to benchmark the cutting
plane solvers with respect to accuracy and speed.

@@

\section{Comparing Learning Algorithms}
%TODO experiments!!

>>>>

Unfortunately only few implementations for learning structured prediction are
publicly available---many applications are based on the non-free implementation
of~\citet{joachims2009cutting}.
In this section, we introduce our implementation, \pystruct, which aims at
providing a high-quality code with an easy-to-use interface, in the high-level
Python language. This allows practitioners to efficiently test a range of
models, as well as allowing researchers to compare to baseline methods much
more easily than this is possible with current implementations. \pystruct is
BSD-licensed, allowing modification and redistribution of the code, as well as
use in commercial applications.  By embracing paradigms established in the
scientific Python community and reusing the interface of the widely-used {\sc
scikit-learn} library~\citep{pedregosa2011scikit}, \pystruct can be used in
existing projects, replacing standard classifiers. The online documentation and
examples help new users understand the somewhat abstract ideas behind
structured prediction.
We base the experiments in the rest of this work on the algorithms
implemented in \pystruct. In the following, we briefly discuss implementation
and features of the \pystruct library.

\subsection{Library Structure and Content}
Using the formulation of structured prediction introduced in
\Secref{basics_structured_prediction}, learning can be broken down into three
sub-problems:
\begin{enumerate*}
    \item Encoding the structure of the problem in a joint feature function $\Phi$.
    \item Solving the loss-augmented prediction problem in Equation~\eqref{loss_augmentation}.
    \item Optimizing the objective in \Eqref{learning_equation} with respect to $\theta$.
\end{enumerate*}
The first two problems are usually tightly coupled, as the maximization in
Equation~\ref{eq:main_equation} is usually only feasible by exploiting the
structure of $\Phi$, as described in \Secref{factor_graphs}. The last problem,
finding $\theta$, on the other hand, is usually treated as independent.
\pystruct takes an object-oriented approach to decouple the task-dependent
implementation of 2. and 3. from the general algorithms used to solve 1.

Estimating $\theta$ is done in \texttt{learner} classes, which currently
support cutting plane algorithms for structural support vector
machines~(SSVMs), the SZLJSP algorithm for SSVMs,
subgradient methods for SSVMs, the structured perceptron and latent variable
SSVMs. See \Secref{learning_algorithms} for a detailed description of the
algorithms. The cutting plane implementation uses the {\sc cvxopt} package
\citep{dahl2006cvxopt} for quadratic optimization.

@@

Table~\ref{table:comparision_algorithms} and
Table~\ref{table:comparision_models} list learning algorithms and models that
are implemented in \pystruct and compares them to other publicly available
structured prediction libraries.

%TODO what about language / license?
\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccccc}
\toprule
Package       & Cutting Plane& SSGD & SZLJSP & Latent SSVM & Perceptron & ML\\
\cmidrule(r){1-1} \cmidrule(r){2-7}
\pystruct     & \x        & \x   & \x   & \x          & \x         & \o\\
\svmstruct    & \x        & \o   & \o   & \x          & \o         & \o\\
\sc{Dlib}     & \x        & \x   & \o   & \o          & \x         & \o\\
\sc{CRFsuite} & \o        & \o   & \o   & \o          & \x         & \x\\

\bottomrule
\end{tabularx}
    \caption{\label{table:comparision_algorithms}Comparison of learning
        algorithms implemented in popular structured prediction software
        packages. SSGD stochastic subgradient decent learning of SSVMs, SZLJSP is
        as described in \secref{dual_coordinate_descent}, Latent SSVM for latent variable SSVMs, ML for
        maximum likelihood learning.}
\end{table}

@@

\paragraph{Testing}
     \pystruct contains a testing-suite with 80\% line-coverage. It also
     employs continuous integration to ensure stability and a seamless user
     experience.

@@

The source code is shown in Listing 1.
Lines 1-3 declare a model using parametric edge potentials for arbitrary graphs.
Here \texttt{class\_weight} re-weights the hamming loss according to inverse class
frequencies. The parametric pairwise interactions have three features: a
constant feature, color similarity, and relative vertical position. The first two
are declared to be symmetric with respect to the direction of an edge, the last
is antisymmetric. The inference method used is QPBO-fusion moves.  Line 5
creates a \texttt{learner} object that will learn the parameters for the given
model using the $n$-slack cutting plane method, and line 6 performs the actual
learning.  Using this simple setup, we achieve an accuracy of 30.3 on the
validation set following the protocol of \citet{krahenbuhl2012efficient}, who
report 30.2 using a more complex approach. Training the structured model takes
approximately 30 minutes using a single i7 core.

\subsection{Experiments}\label{sec:benchmarks}
While \pystruct focuses on usability and covers a wide range of applications, it is also
important that the implemented learning algorithms run in acceptable time.
In this section, we compare our implementation of the $1$-slack cutting plane
algorithm with the implementation in \svmstruct.
We compare performance of the Crammer-Singer multi-class SVM with respect to
learning time and accuracy on the MNIST dataset of handwritten digits.
While multi-class classification is not very interesting from a structured
prediction point of view, this problem is well-suited to benchmark the cutting
plane solvers, as loss-augmented prediction is trivial.

@@

%\section{Comparing Learning Algorithms}
%TODO experiments!!
